Measurement and Probability in Fuzzy Quantum Theories

### 2017-05-03 prop_iop.tex
prop_iop.tex \subsection{Describe Classical World by Quantum Probability Measures with a Commuting Sub-event Space} Updating...

\begin{proof}Again, it is sufficient to prove the interval-valued
case. Since $\events'$ is a set of mutually orthogonal projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a quantum interval-valued probability
measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}

@@

Since there is a correspondence between classical probability measures
and quantum ones on a commuting sub-event space, we can use the quantum
language to describe the classical world given a commuting sub-event
space.

@@

Intuitively, the expectation value of an observable with respect to
an IVPM should be the minimum and maximum expectation value of the
same observable with respect to its consistent states. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space, whose definition is given in the next subsection.

\noindent Having these two definition, we can write down our idea
formally as follow.

>>>>

\begin{proof}Again, it is sufficient to prove the interval-valued
case. Since $\events'$ is a set of mutually commuting projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$.
By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a quantum interval-valued probability
measure by lemma~\ref{lemma:classical-probability-measures}.\end{proof}

@@

Since there is a correspondence between classical probability measures
and quantum ones on a commuting sub-event space, we can use the quantum
language to describe the classical world given an orthonormal basis.

\begin{definition}Given a Hilbert space~$\Hilb$, an orthonormal
basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$, a classical
real-valued probability measures~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
on the sample space~$\Omega$. The density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}$
is call classical with respect to $\Omega$.\end{definition}

Then, we can rephrase theorem~\ref{thm:Shapley}, in the language
of quantum IVPM with an orthonormal basis.

\begin{cor}For every convex quantum IVPM~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if $\events'$ commutes, then $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{cor}

\begin{proof}Since $\events'$ is a set of mutually commuting projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
and we can find a function~$\tau:\events'\rightarrow2^{\Omega}$
such that the condition of theorem~\ref{thm:sub-event-space} holds.
This means that we can find a convex classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. By theorem~\ref{thm:Shapley}, there is
a. classical probability measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$
such that $\pmeas\in\mathrm{core}\left(\bar{\mu}'\right)$. Then,
it is easy to verify that the density matrix~$\sum_{j=0}^{d-1}\pmeas\left(\left\{ j\right\} \right)\proj{j}\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

@@

Intuitively, the expectation value of an observable with respect to
an IVPM should be the minimum and maximum expectation value of the
same observable with respect to its consistent states. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space.
